---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rDTM

<!-- badges: start -->
<!-- badges: end -->

The goal of rDTM is to provide a easy way to get the data from [IOM's Displacement Tracking Matrix (DTM) API](https://dtm.iom.int/data-and-analysis/dtm-api).This API allows the humanitarian community, academia, media, government, and non-governmental organizations to utilize the data collected by DTM. The DTM API only provides non-sensitive IDP figures, aggregated at the country, Admin 1 (states, provinces, or equivalent), and Admin 2 (smaller subnational administrative areas) levels.

## Installation

You can install the development version of rDTM from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jxaaa/rDTM")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rDTM)
#Retrieve the Global IDP Data Country Level for Afghanistan from Jan 2000 to May 2024, and convert output as Dataframe.
result <- countryLevelData(countryName="Afghanistan", monthFrom_month= "1", monthFrom_year=2000, monthTo_month= "5", monthTo_year=2024,to_dataframe =TRUE)

#Retrieve the Global IDP Data at Admin 1 Level for Afghanistan from Jan 2000 to May 2024, and convert output as Dataframe.
result <- admin1LevelData(countryName="Afghanistan", monthFrom_month= "1", monthFrom_year=2000, monthTo_month= "5", monthTo_year=2024,to_dataframe =TRUE)

#Retrieve the Global IDP Data at Admin 2 Level for Afghanistan from Jan 2000 to May 2024, and convert output as Dataframe.
result <- admin2LevelData(countryName="Afghanistan", monthFrom_month= "1", monthFrom_year=2000, monthTo_month= "5", monthTo_year=2024,to_dataframe =TRUE)

```

